---
title: "Introduction to christmaswrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to christmaswrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(christmaswrap)
```

The christmaswrap package wraps the [christmascountdown API](https://christmascountdown.live/api) and provides access to each of the endpoints.

## Get your kids excited about data science early with Christmas-themed plots!
The `period_left()` function can be used to get the time left until Christmas in a variety of different time units. For this plot, we'll use the time unit "sleeps".  
```{r}
# Use period_left to get sleeps left until Christmas
sleeps_left <- period_left("sleeps", timezone = "PST")

# Calculate sleeps completed so far
sleeps_done <- 365 - sleeps_left
```

To make the plot a bit more fun, we can add a joke to the plot. The `joke()` function can be used to get a random Christmas-themed joke.
```{r}
# Get fun joke to spice up the plot
joke <- joke()

# Plot time until Christmas
pie(
  c(sleeps_done, sleeps_left),
  labels = c("", "Sleeps Left"),
  col = c("darkgreen", "red3"),
  main = joke$question,
  sub = joke$answer
)
```

If we aren't happy with a random joke, we can use the `all_jokes()` function to get all possible jokes and choose a specific one.  
```{r}
jokes <- all_jokes()
jokes[[90]]
```

Maybe we want to plot each time unit. The `time_left()` function allows us to get all time units with one request. For this example we're going to use a log scale to allow us to see all the units better.  
```{r}
# Get time left in each time unit
all_times_left <- time_left()

# Plot each time unit
barplot(
  unname(unlist(all_times_left)),
  names.arg = names(all_times_left),
  log = 'y',
  col = c("darkgreen", "red3")
)
```

We can also use a similar plot to show the exact time left until Christmas. The previous time left functions allowed us to get the time until Christmas in a single time unit. The `total_time_left()` function allows us to get the time left until Christmas using multiple time units.  
```{r}
time_til_christmas <- total_time_left()

barplot(
  unname(unlist(time_til_christmas)),
  names.arg = names(time_til_christmas),
  col = c("darkgreen", "red3")
)
```

